Supplemental Material: Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling.

### 2020-01-28 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Update supporting info.
fixed supporting and PDFs.

  \maketitle
  \tableofcontents
  \graphicspath{{./supporting_figures/}}
  \bibliographystyle{ieeetr}

@@

  We collected all data used for model generation after the solutes were 
  equilibrated. We assumed a solute to be equilibrated when the partition of
  solutes in and out of the pore region stopped changing. The pore region is
  defined as within 0.75 nm of the pore center. We've plotted the partition
  versus time in Figure~\ref{fig:equilibration} and indicated the chosen
  equilibration time points.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{URE_counts.pdf}
  \caption{Urea}\label{fig:URE_counts}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{GCL_counts.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_counts}
  \end{subfigure}
  \caption{The number of transitions from state $i$ to $j$ and $j$ to $i$ are very close
  indicating that our process obeys detailed balance. Detailed balance is conserved for 
  different sized time steps.}\label{fig:counts}
  %MRS: would this be clearer to see if you plotted i-j/i+j for a relative error to see how different it is from symmetric jumps? 
  \end{figure}

@@

  When we use a pure power law distribution to parameterize the dwell time 
  distributions of the 1 and 2 mode AD models, the MD MSDs are severely 
  under-predicted because we are incorporating dwell times on the order of 
  the simulation length into simulated trajectories 
  (see Figure~\ref{fig:anomalous_msds_bothmode}). The parameters of the pure power law 
   distribution are included in Figure~\ref{fig:pure_power_law_params}.

@@

  We validated both the 1 and 2 mode AD models with urea and acetic acid, since their
  trajectories appear stationary. The MSDs resulting from 1000 realizations of the AD
  model are shown in Figure~\ref{fig:train_test}. We consider the model's prediction 
  to match well if the MSD lies within the 1$\sigma$ confidence intervals of the MD MSDs.
  We also look for qualitative agreement in the shape of the curves.

  The models are capable of reasonably predicting the MD MSD values of the second
  half of the solute trajectories based on parameters generated from the first half
  when the dwell time distributions are parameterized by a power law with an 
  exponential cut-off. At long timescales, the MSD of urea is under-predicted 
  for both the 1 and 2 mode models with the same true of acetic acid on short 
  timescales. Without truncation of the power law distribution, the MD 
  MSDs are underestimated in all cases because dwell times on the order of the
  MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories.

@@

% LocalWords:  LLC solutes py equispaced solute's ctrw sfbm ctrwsim MSD solute
% LocalWords:  MSDDM XXXX GitHub plateaued Meroz Sokolov superdiffusion MSDs wt
% LocalWords:  subdiffusion msd PR nojump xtc gro ETH nboot pdf subdiffusive xr
% LocalWords:  RWF brownian FBM CTRWs traj npt fracshow Taqqu recentering MFPT
% LocalWords:  Markovianity timestep GCL acf ACH bothmode params BJC tex acid's
% LocalWords:  sFBMcut sFLMcut urea's timescale msddm fpt CDF mfpt cdf hurst
% LocalWords:  decorrelate

>>>>

  \maketitle
  %MRS10: be consistent on capitalization of section titles (And therefore table of contents)
  \tableofcontents
  \graphicspath{{./supporting_figures/}}
  \bibliographystyle{ieeetr}

@@

  We collected all data used for model generation after the solutes were 
  equilibrated. We assumed a solute to be equilibrated when the partition of
  solutes in and out of the pore region stopped changing. The pore region is
  defined as within 0.75 nm of the pore center. We plot the partition
  versus time in Figure~\ref{fig:equilibration} and indicated the chosen
  equilibration time points.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{URE_counts.pdf}
  \caption{Urea}\label{fig:URE_counts}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{GCL_counts.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_counts}
  \end{subfigure}
  \caption{The number of transitions from state $i$ to $j$ and $j$ to $i$ are very close
  indicating that our process obeys detailed balance. Detailed balance is conserved for 
  different sized time steps.}\label{fig:counts}
  %MRS10: be clear why the graph shows detailed balance in the caption.
  %MRS: would this be clearer to see if you plotted i-j/i+j for a relative error to see how different it is from symmetric jumps? 
  \end{figure}

@@

  When we use a pure power law distribution to parameterize the dwell time 
  distributions of the one and two mode AD models, the MD MSDs are severely 
  under-predicted because we are incorporating dwell times on the order of 
  the simulation length into simulated trajectories 
  (see Figure~\ref{fig:anomalous_msds_bothmode}). The parameters of the pure power law 
   distribution are included in Figure~\ref{fig:pure_power_law_params}.

@@

  We validated both the one and two mode AD models with urea and acetic acid, since their
  trajectories appear stationary. The MSDs resulting from 1000 realizations of the AD
  model are shown in Figure~\ref{fig:train_test}. We consider the model's prediction 
  to match well if the MSD lies within the 1$\sigma$ confidence intervals of the MD MSDs.
  We also look for qualitative agreement in the shape of the curves.

  The models are capable of reasonably predicting the MD MSD values of the second
  half of the solute trajectories based on parameters generated from the first half
  when the dwell time distributions are parameterized by a power law with an 
  exponential cut-off. At long timescales, the MSD of urea is under-predicted 
  for both the one and two mode models with the same true of acetic acid on short 
  timescales. Without truncation of the power law distribution, the MD 
  MSDs are underestimated in all cases because dwell times on the order of the
  MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories.

@@

% LocalWords:  LLC solutes py equispaced solute's ctrw sfbm ctrwsim MSD solute
% LocalWords:  MSDDM XXXX GitHub plateaued Meroz Sokolov superdiffusion MSDs wt
% LocalWords:  subdiffusion msd PR nojump xtc gro ETH nboot pdf subdiffusive xr
% LocalWords:  RWF brownian FBM CTRWs traj npt fracshow Taqqu recentering MFPT
% LocalWords:  Markovianity timestep GCL acf ACH bothmode params BJC tex acid's
% LocalWords:  sFBMcut sFLMcut urea's timescale msddm fpt CDF mfpt cdf hurst
% LocalWords:  decorrelate nanopore FLM autocovariance evy undersampling Stoev
% LocalWords:  undersampled URE timescales Nsensitivity Asensitivity
% LocalWords:  betasensitivity
